\vspace{-1.5cm} \textbf{STA610 Case Study 1 Team 4 Report}

### 2021-03-22 final_report_2.Rmd
Formatting changes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.height = 3)
```

@@

```{r}
# Test date_num
drop_date_num <- anova(mod_s,
      lmer(data=df, log_ppm ~ (1 |state) + date_quarter + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F))
date_num_pval <- drop_date_num$`Pr(>Chisq)`[2]
# Test date_quarter
drop_quarter <- anova(lmer(data=df, log_ppm ~ (1 |state) + date_quarter + dose_per_mg + 
                    bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F))
quarter_pval <- drop_quarter$`Pr(>Chisq)`[2]
# Test dose_per_mg
drop_dose <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + bulk_purchase + Primary_Reason + source, REML=F))
dose_pval <- drop_dose$`Pr(>Chisq)`[2]
# Test bulk purchase
drop_bulk <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + Primary_Reason + source, REML=F))
bulk_pval <- drop_bulk$`Pr(>Chisq)`[2]
# Test primary reason
drop_reason <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + source, REML=F))
reason_pval <- drop_reason$`Pr(>Chisq)`[2]
# Test source
drop_source <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason, REML=F))
source_pval <- drop_source$`Pr(>Chisq)`[2]
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.height = 3, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

@@

```{r}
# Test date_num
drop_date_num <- anova(mod_s,
      lmer(data=df, log_ppm ~ (1 |state) + date_quarter + dose_per_mg + 
               bulk_purchase + Primary_Reason + source, REML=F))
date_num_pval <- drop_date_num$`Pr(>Chisq)`[2]
# Test date_quarter
drop_quarter <- anova(lmer(data=df, log_ppm ~ (1 |state) + 
                        date_quarter + dose_per_mg +
                        bulk_purchase + Primary_Reason + source, REML=F),
                lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + 
                         bulk_purchase + Primary_Reason + source, REML=F))
quarter_pval <- drop_quarter$`Pr(>Chisq)`[2]

# Test dose_per_mg
drop_dose <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + 
                        bulk_purchase + Primary_Reason + source, REML=F),
                   lmer(data=df, log_ppm ~ (1 |state) + bulk_purchase 
                        + Primary_Reason + source, REML=F))
dose_pval <- drop_dose$`Pr(>Chisq)`[2]

# Test bulk purchase
drop_bulk <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + 
                        bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + 
               Primary_Reason + source, REML=F))
bulk_pval <- drop_bulk$`Pr(>Chisq)`[2]

# Test primary reason
drop_reason <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + 
                              bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + 
               bulk_purchase + source, REML=F))
reason_pval <- drop_reason$`Pr(>Chisq)`[2]

# Test source
drop_source <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + 
                              bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + 
               bulk_purchase + Primary_Reason, REML=F))
source_pval <- drop_source$`Pr(>Chisq)`[2]
```
